Expected Dependency Pair Match: Predicting translation quality with expected syntactic structure

### 2009-08-02 reviewers/review-response.tex

% -*- LaTeX -*-
\documentclass[letterpaper,12pt]{article}

\newenvironment{response}
{\begin{quotation} \bf}
  {\end{quotation}}

\begin{document}

\section{Comments for the Author: Reviewer \#1}
\label{sec:reviewer1}

This submission on Dependency Pair Match MT metrics is technically and
structurally sound, thorough, and well-written.  Some specific
comments/questions below, in order of appearance in the paper.
\begin{response}
  Thank you for this feedback. Our responses are below.
\end{response}
As per the submission guidelines, submissions must be limited to 12
pages of content, with an additional page for references.  The current
version has 16.5 pages plus one page of references, so significant
shortening will be necessary.  I find the overall balance of sections
adequate, so I would recommend shortening across the board rather than
in one particular section.
\begin{response}
  We have done revisions to compress and simplify the writing
  throughout the paper to address the length concerns.
\end{response}
While likely known by most of the community, I would recommend
expanding all acronyms the first time (LFG, PCFG, ...).

In section 2, ``bag of dependent word'' should be ``bag of dependent
word*s*''.
\begin{response}
  We believe that we have emended these.
\end{response}
Can you expand on the reasoning behind the modifications to the
Charniak parser rules described in section 3.1?
\begin{response}
  We hope that our examples (and some additional explanatory sentences
  in section 3) have addressed this concern.
\end{response}
In section 4.1, while the corpus is referenced and the information can
be looked up, it would still be helpful to include directly in the
paper a brief description of the adequacy and fluency measures.  In
particular, what kind (granularity) of scale was used for the
judgments needs to be known in order to be able to assess the reported
correlations.  A brief description of the data genre(s) would be
useful to have at hand as well.  Also, I assume you correlate at the
*segment* level, but this is not explicitly stated.
\begin{response}
  Section 4 has now included several additional sentences to clarify
  these points.
\end{response}
The correlations reported in section 4 (tables I-III) are overall
quite low (also compared to EDPM's r correlations for Chinese source
data in NIST's MetricsMATR challenge).  Could you comment on this?
\begin{response} [TO DO]
\end{response}
For ease of lookup, please include in the table headings for tables
I-III that the correlations are with human judgments of adequacy and
fluency

In section 5.1, ``EDPM's strengths, relative to the other measures, are
particularly clear in the unstructured domains (wb and bc).''  This
statement does not seem to hold for EDPM vs. BLEU for the wb genre in
table Va; the correlation reported is the same for the two metrics?

\section{Comments for the Author: Reviewer \#2}
\label{sec:reviewer2}

This article presents a method for evaluating MT system hypotheses
that is based on complete and partial dependency triple matches
between hypothesis and reference translation.

The paper is well motivated, clearly written, and presents interesting
results. On my opinion, it is suitable for publication with minor
revisions. My main points of criticism are:

- It is considerably too long. Papers are supposed to be 12 pages +
 references; this paper has more than 16 pages. I recommend
 (a) shortening the introduction; (b) shortening the discussion
 of the "model space" in Sections 2/3 somewhat; (c) removing the
 third experiment (Section 6), whose contribution is unclear to
 me, altogether. (see below for details)

- On the other hand, the paper does not motivate at all what the
 intuition behind the use of dependency triple match is. Why
 should we assume in the first place that dependency triples
 predict human judgments better than (e.g.) n-grams?

- Finally, the paper does not give a single example. In a paper
 about a novel evaluation metric, I would like to get a feeling
 for what it is that the new metric does better than existing
 metrics. (This can be addressed together with the previous point.)

Detail comments:

- The discussion on page 2 reads nicely, but is probably too
 extensive -- in particular for a paper aimed at a special
 issue where there will presumably be an overview article
 that discusses relevant previous work.

- p.2, publically -> publicly?

- p.3, "In section 2 etc." I'm not sure that a 12-page paper requires
 a table of contents.

- p.3, reference to Owczarzak et al.'s work. In particular since their
 work has also appeared in the MT journal (please update the
 reference, btw!), it would be good to expand on the similarities and
 differences of your work and theirs.

-p.4 I'm not so sure that I believe in the benefit of overweighting.
 In standard dependency graphs, for example, modifications are usually
 dependendents of the head and are thus "underweighted" by your scheme,
 but modifiers like negations etc. can considerably change the meaning.
 (You write "we argue" but I don't see an argument, just a claim --
  details of counts for an example might be helpful.)

-p.5 "When multiple decompositions etc." As far as I can see, you
 get consistently better scores for F[] than for $\mu_{PR}[]$ throughout
 your experiments.  I'd suggest reducing the discussion of $\mu$ here
 and in Section 3.2 with a short explanation that $\mu$ has been found to
 work worse than F.

- p.6 "LFG...heavily knowledge-engineered parser". I think you're being
 overly harsh on the LFG-based work here. As the title of the paper you
 cite says, you're talking about an "automatically acquired PCFG-based
 LFG approximation" that's learned from a treebank, so you are really
 very much in the same boat.

- p.7 "Score combination" - see comment above
     "Tuned, like the ..." - ungrammatical sentence?

- Evaluation (p. 8) In principle I like the idea of teasing apart
 sentence difficulty and translation quality. However, I have two
 reservations: (1), you are losing comparability of scores across
 sentences; and (2), you are committing to a scenario where you
 always have access to a sufficient number of translations in order
 to estimate the mean score. In other words, in the limit of one
 system, you do not predict anything.  These issues should be
 mentioned and discussed.  (Note about presentation: you don't
 introduce the variable t in Equation 3 -- I guess this is the
 segment?)

 More generally, I would like to see a motivation for the evaluation
 you perform. You seem to largely follow Owczarzak et al's
 evaluation, e.g. in the choice of data (Section 4.1), but you depart
 from it in some crucial respects (e.g. the definition of the
 dependent variable by mean subtraction). Can you provide a clearer
 description of why each experiment is set up in the way it is?

- p.10 Am I right in reading Table II to say that F always outperforms
 BLEU, but $\mu$ never does? Maybe it would be good to re-mention the
 BLEU results in Table II.

- p.12 Can you elaborate on why you want to weight per-sentence
 correlations by sentence length? I don't feel that this
 appropriate. After all, I'd think that you are not \emph{more} interested
 in longer sentences, but you want each sentence to have the same
 contribution to the analysis. I assume the problem is that there is
 considerably more variance for shorter sentence, which is alleviated
 by length-based weighting, but to me this reads like a cover-up. If
 you have good arguments for wanting long sentences to count more in
 the analysis, I'd be interested to hear them.

- Section 6. To my mind, this is the least convincing section of the
 paper. The experiments in Section 4 have already shown that a simple
 F-score-based combination of the different matches does better than
 considering individual components. While I agree that this might be
 a weighting problem, this experiment shows basically a null result.
 From what I can gather from Figure 4, TERp on its own does
 (significantly?) better than EDPM, and their combination doesn't
 really improve a lot. I acknowledge the positive result that there
 is no \emph{decrease} in performance either, but then you're using quite
 a lot of data (50\% = 2500 sentences) for tuning so that is to be
 expected. I would very much like to see how robust the tuning
 process is to smaller development sets, but that would require even
 more space.

 In sum, I'd suggest replacing Section 6 with some actual examples
 and more discussion of the methodical points I have suggested.
\end{document}

### 2009-08-02 reviewers/review-response.tex

\section{Comments for the Author: Reviewer \#2}
\label{sec:reviewer2}

This article presents a method for evaluating MT system hypotheses
that is based on complete and partial dependency triple matches
between hypothesis and reference translation.

The paper is well motivated, clearly written, and presents interesting
results. On my opinion, it is suitable for publication with minor
revisions. My main points of criticism are:

\begin{itemize}
\item It is considerably too long. Papers are supposed to be 12 pages
  + references; this paper has more than 16 pages. I recommend (a)
  shortening the introduction; (b) shortening the discussion of the
  ``model space'' in Sections 2/3 somewhat; (c) removing the third
  experiment (Section 6), whose contribution is unclear to me,
  altogether. (see below for details)

\item On the other hand, the paper does not motivate at all what the
  intuition behind the use of dependency triple match is. Why should
  we assume in the first place that dependency triples predict human
  judgments better than (e.g.) n-grams?

\item Finally, the paper does not give a single example. In a paper
  about a novel evaluation metric, I would like to get a feeling for
  what it is that the new metric does better than existing
  metrics. (This can be addressed together with the previous point.)
\end{itemize}

@@

Detail comments:

\begin{itemize}
\item The discussion on page 2 reads nicely, but is probably too
  extensive -- in particular for a paper aimed at a special issue
  where there will presumably be an overview article that discusses
  relevant previous work.

\item  p.2, publically $\to$ publicly?

\item  p.3, ``In section 2 etc.'' I'm not sure that a 12-page paper
  requires a table of contents.

\item  p.3, reference to Owczarzak et al.'s work. In particular since
  their work has also appeared in the MT journal (please update the
  reference, btw!), it would be good to expand on the similarities and
  differences of your work and theirs.

\item p.4 I'm not so sure that I believe in the benefit of overweighting.
  In standard dependency graphs, for example, modifications are
  usually dependendents of the head and are thus ``underweighted'' by
  your scheme, but modifiers like negations etc. can considerably
  change the meaning.  (You write ``we argue'' but I don't see an
  argument, just a claim -- details of counts for an example might be
  helpful.)

\item p.5 ``When multiple decompositions etc.'' As far as I can see, you
  get consistently better scores for F[] than for $\mu_{PR}[]$
  throughout your experiments.  I'd suggest reducing the discussion of
  $\mu$ here and in Section 3.2 with a short explanation that $\mu$
  has been found to work worse than F.

\item  p.6 ``LFG...heavily knowledge-engineered parser''. I think you're
  being overly harsh on the LFG-based work here. As the title of the
  paper you cite says, you're talking about an ``automatically acquired
  PCFG-based LFG approximation'' that's learned from a treebank, so you
  are really very much in the same boat.

\item p.7 ``Score combination'' --- see comment above

\item ``Tuned, like the ...''  --- ungrammatical sentence?

\item  Evaluation (p. 8) In principle I like the idea of teasing apart
  sentence difficulty and translation quality. However, I have two
  reservations: (1), you are losing comparability of scores across
  sentences; and (2), you are committing to a scenario where you
  always have access to a sufficient number of translations in order
  to estimate the mean score. In other words, in the limit of one
  system, you do not predict anything.  These issues should be
  mentioned and discussed.  (Note about presentation: you don't
  introduce the variable t in Equation 3 -- I guess this is the
  segment?)

@@

  More generally, I would like to see a motivation for the evaluation
  you perform. You seem to largely follow Owczarzak et al's
  evaluation, e.g. in the choice of data (Section 4.1), but you depart
  from it in some crucial respects (e.g. the definition of the
  dependent variable by mean subtraction). Can you provide a clearer
  description of why each experiment is set up in the way it is?

\item  p.10 Am I right in reading Table II to say that F always
  outperforms BLEU, but $\mu$ never does? Maybe it would be good to
  re-mention the BLEU results in Table II.

\item  p.12 Can you elaborate on why you want to weight per-sentence
  correlations by sentence length? I don't feel that this
  appropriate. After all, I'd think that you are not \emph{more}
  interested in longer sentences, but you want each sentence to have
  the same contribution to the analysis. I assume the problem is that
  there is considerably more variance for shorter sentence, which is
  alleviated by length-based weighting, but to me this reads like a
  cover-up. If you have good arguments for wanting long sentences to
  count more in the analysis, I'd be interested to hear them.

\item  Section 6. To my mind, this is the least convincing section of the
  paper. The experiments in Section 4 have already shown that a simple
  F-score-based combination of the different matches does better than
  considering individual components. While I agree that this might be
  a weighting problem, this experiment shows basically a null result.
  From what I can gather from Figure 4, TERp on its own does
  (significantly?) better than EDPM, and their combination doesn't
  really improve a lot. I acknowledge the positive result that there
  is no \emph{decrease} in performance either, but then you're using
  quite a lot of data (50\% = 2500 sentences) for tuning so that is to
  be expected. I would very much like to see how robust the tuning
  process is to smaller development sets, but that would require even
  more space.
\end{itemize}
 In sum, I'd suggest replacing Section 6 with some actual examples
 and more discussion of the methodical points I have suggested.
\end{document}

### 2009-08-04 reviewers/review-response.tex

% -*- LaTeX -*-
\documentclass[letterpaper,12pt]{article}

\newenvironment{response}
{\begin{quotation} \it}
  {\end{quotation}}

@@

\begin{document}

\section{Comments for the Author: Reviewer \#1}
\label{sec:reviewer1}

This submission on Dependency Pair Match MT metrics is technically and
structurally sound, thorough, and well-written.  Some specific
comments/questions below, in order of appearance in the paper.
\begin{response}
  Thank you for this feedback. Our responses are below.
\end{response}
As per the submission guidelines, submissions must be limited to 12
pages of content, with an additional page for references.  The current
version has 16.5 pages plus one page of references, so significant
shortening will be necessary.  I find the overall balance of sections
adequate, so I would recommend shortening across the board rather than
in one particular section.
\begin{response}
  We have done revisions to compress and simplify the writing
  throughout the paper to address the length concerns.
\end{response}
While likely known by most of the community, I would recommend
expanding all acronyms the first time (LFG, PCFG, ...).

In section 2, ``bag of dependent word'' should be ``bag of dependent
word*s*''.
\begin{response}
  We believe that we have emended these.
\end{response}
Can you expand on the reasoning behind the modifications to the
Charniak parser rules described in section 3.1?
\begin{response}
  We hope that our examples (and some additional explanatory sentences
  in section 3) have addressed this concern.
\end{response}
In section 4.1, while the corpus is referenced and the information can
be looked up, it would still be helpful to include directly in the
paper a brief description of the adequacy and fluency measures.  In
particular, what kind (granularity) of scale was used for the
judgments needs to be known in order to be able to assess the reported
correlations.  A brief description of the data genre(s) would be
useful to have at hand as well.  Also, I assume you correlate at the
*segment* level, but this is not explicitly stated.
\begin{response}
  Section 4 has now included several additional sentences to clarify
  these points.
\end{response}
The correlations reported in section 4 (tables I-III) are overall
quite low (also compared to EDPM's r correlations for Chinese source
data in NIST's MetricsMATR challenge).  Could you comment on this?
\begin{response}
 [TO DO]
\end{response}
For ease of lookup, please include in the table headings for tables
I-III that the correlations are with human judgments of adequacy and
fluency
\begin{response}
  This suggestion has been included in the revised table headings.
\end{response}

In section 5.1, ``EDPM's strengths, relative to the other measures, are
particularly clear in the unstructured domains (wb and bc).''  This
statement does not seem to hold for EDPM vs. BLEU for the wb genre in
table Va; the correlation reported is the same for the two metrics?
\begin{response}
  [TO DO]
\end{response}

@@

\section{Comments for the Author: Reviewer \#2}
\label{sec:reviewer2}

This article presents a method for evaluating MT system hypotheses
that is based on complete and partial dependency triple matches
between hypothesis and reference translation.

The paper is well motivated, clearly written, and presents interesting
results. On my opinion, it is suitable for publication with minor
revisions. My main points of criticism are:

\begin{itemize}
\item It is considerably too long. Papers are supposed to be 12 pages
  + references; this paper has more than 16 pages. I recommend (a)
  shortening the introduction; (b) shortening the discussion of the
  ``model space'' in Sections 2/3 somewhat; (c) removing the third
  experiment (Section 6), whose contribution is unclear to me,
  altogether. (see below for details)
  \begin{response}
    Our revisions incorporate many of these suggestions. Rather than
    eliminate section 6, we have chosen to compress it, but we have
    adopted the rest of the suggestions above.
  \end{response}

\item On the other hand, the paper does not motivate at all what the
  intuition behind the use of dependency triple match is. Why should
  we assume in the first place that dependency triples predict human
  judgments better than (e.g.) n-grams?
  \begin{response}
    [TO DO -- using motivating examples?]
  \end{response}

\item Finally, the paper does not give a single example. In a paper
  about a novel evaluation metric, I would like to get a feeling for
  what it is that the new metric does better than existing
  metrics. (This can be addressed together with the previous point.)
  \begin{response}
    [TO DO -- again using motivating examples?]
  \end{response}
\end{itemize}

@@

Detail comments:

\begin{itemize}
\item The discussion on page 2 reads nicely, but is probably too
  extensive -- in particular for a paper aimed at a special issue
  where there will presumably be an overview article that discusses
  relevant previous work.
  \begin{response}
    Thank you for pointing this out. We have squeezed this discussion
    considerably.
  \end{response}

\item  p.2, publically $\to$ publicly?
  \begin{response}
    This spelling error has been corrected.
  \end{response}

\item  p.3, ``In section 2 etc.'' I'm not sure that a 12-page paper
  requires a table of contents.
  \begin{response}
    This section has also been compressed.
  \end{response}

\item  p.3, reference to Owczarzak et al.'s work. In particular since
  their work has also appeared in the MT journal (please update the
  reference, btw!), it would be good to expand on the similarities and
  differences of your work and theirs.
  \begin{response}
    [TO DO].  The reference has been updated.
  \end{response}

\item p.4 I'm not so sure that I believe in the benefit of overweighting.
  In standard dependency graphs, for example, modifications are
  usually dependendents of the head and are thus ``underweighted'' by
  your scheme, but modifiers like negations etc. can considerably
  change the meaning.  (You write ``we argue'' but I don't see an
  argument, just a claim -- details of counts for an example might be
  helpful.)
  \begin{response}
    [TO DO: motivating examples?]
  \end{response}

\item p.5 ``When multiple decompositions etc.'' As far as I can see, you
  get consistently better scores for F[] than for $\mu_{PR}[]$
  throughout your experiments.  I'd suggest reducing the discussion of
  $\mu$ here and in Section 3.2 with a short explanation that $\mu$
  has been found to work worse than F.
  \begin{response}
    [TO DO] reduce the discussion of $\mu_{PR}$ further?
  \end{response}

\item  p.6 ``LFG...heavily knowledge-engineered parser''. I think you're
  being overly harsh on the LFG-based work here. As the title of the
  paper you cite says, you're talking about an ``automatically acquired
  PCFG-based LFG approximation'' that's learned from a treebank, so you
  are really very much in the same boat.
  \begin{response}
    Both are indeed built off treebanks, so the knowledge-engineering
    is similar. The contrast is in fact between a more ``surface''
    syntactic representation (the PCFG model) or a ``deeper'', more
    semantic one, and the discussion has been changed to reflect this.
  \end{response}

\item p.7 ``Score combination'' --- see comment above 
  \begin{response}
    [TO DO]
  \end{response}

\item ``Tuned, like the ...''  --- ungrammatical sentence?
  \begin{response}
    This bullet's wording has been clarified.
  \end{response}

\item  Evaluation (p. 8) In principle I like the idea of teasing apart
  sentence difficulty and translation quality. However, I have two
  reservations: (1), you are losing comparability of scores across
  sentences; and (2), you are committing to a scenario where you
  always have access to a sufficient number of translations in order
  to estimate the mean score. In other words, in the limit of one
  system, you do not predict anything.  These issues should be
  mentioned and discussed.  
  \begin{response}
    [TO DO]
  \end{response}
  (Note about presentation: you don't
  introduce the variable $t$ in Equation 3 -- I guess this is the
  segment?)
  \begin{response}
    Thank you! this oversight is now repaired and $t$ is explicit.
  \end{response}

  More generally, I would like to see a motivation for the evaluation
  you perform. You seem to largely follow Owczarzak et al's
  evaluation, e.g. in the choice of data (Section 4.1), but you depart
  from it in some crucial respects (e.g. the definition of the
  dependent variable by mean subtraction). Can you provide a clearer
  description of why each experiment is set up in the way it is?
  \begin{response}
    Section 4 is intended to match the Owczarzak \textit{et al.} data
    selection, but sections 5 and 6 do not; in sections 5 and 6 the
    data available \emph{does} allow multiple translations of the same
    segment and thus we can use mean-subtraction. Mean subtraction is
    only used in sections 5 and 6, and the discussion of
    mean-subtraction has been moved to the beginning of section 5 for
    clarity.
  \end{response}

\item  p.10 Am I right in reading Table II to say that F always
  outperforms BLEU, but $\mu$ never does? Maybe it would be good to
  re-mention the BLEU results in Table II.
  \begin{response}
    [TO DO]
  \end{response}

\item  p.12 Can you elaborate on why you want to weight per-sentence
  correlations by sentence length? I don't feel that this
  appropriate. After all, I'd think that you are not \emph{more}
  interested in longer sentences, but you want each sentence to have
  the same contribution to the analysis. I assume the problem is that
  there is considerably more variance for shorter sentence, which is
  alleviated by length-based weighting, but to me this reads like a
  cover-up. If you have good arguments for wanting long sentences to
  count more in the analysis, I'd be interested to hear them.
  \begin{response}
    [TO DO]
  \end{response}

\item  Section 6. To my mind, this is the least convincing section of the
  paper. The experiments in Section 4 have already shown that a simple
  F-score-based combination of the different matches does better than
  considering individual components. While I agree that this might be
  a weighting problem, this experiment shows basically a null result.
  From what I can gather from Figure 4, TERp on its own does
  (significantly?) better than EDPM, and their combination doesn't
  really improve a lot. I acknowledge the positive result that there
  is no \emph{decrease} in performance either, but then you're using
  quite a lot of data (50\% = 2500 sentences) for tuning so that is to
  be expected. I would very much like to see how robust the tuning
  process is to smaller development sets, but that would require even
  more space.
\end{itemize}
In sum, I'd suggest replacing Section 6 with some actual examples and
more discussion of the methodical points I have suggested.
\begin{response}
  [TO DO]: We have made a number of changes to section 6.  We have
  revisited the two-fold validation and provided a new statistical
  analysis that simplifies both the presentation (figure 4) and the
  discussion (elsewhere in section 6).
\end{response}
\end{document}

### 2009-08-05 reviewers/review-response.tex

\newenvironment{response}
{\begin{quotation} \it}
  {\end{quotation}}

\begin{document}

\section{Comments for the Author: Reviewer \#1}
\label{sec:reviewer1}

This submission on Dependency Pair Match MT metrics is technically and
structurally sound, thorough, and well-written.  Some specific
comments/questions below, in order of appearance in the paper.
\begin{response}
  Thank you for this feedback. Our responses are below.
\end{response}
As per the submission guidelines, submissions must be limited to 12
pages of content, with an additional page for references.  The current
version has 16.5 pages plus one page of references, so significant
shortening will be necessary.  I find the overall balance of sections
adequate, so I would recommend shortening across the board rather than
in one particular section.
\begin{response}
  We have done revisions to compress and simplify the writing
  throughout the paper to address the length concerns.
\end{response}
While likely known by most of the community, I would recommend
expanding all acronyms the first time (LFG, PCFG, ...).
\begin{response}
  Done.
\end{response}

In section 2, ``bag of dependent word'' should be ``bag of dependent
word*s*''.
\begin{response}
  Done.
\end{response}
Can you expand on the reasoning behind the modifications to the
Charniak parser rules described in section 3.1?
\begin{response}
  We added discussion in section 3 and refer back to the example in
  section two, which illustrates this point. [TO DO -- emend the discussion].
\end{response}
In section 4.1, while the corpus is referenced and the information can
be looked up, it would still be helpful to include directly in the
paper a brief description of the adequacy and fluency measures.  In
particular, what kind (granularity) of scale was used for the
judgments needs to be known in order to be able to assess the reported
correlations.  A brief description of the data genre(s) would be
useful to have at hand as well.  Also, I assume you correlate at the
*segment* level, but this is not explicitly stated.
\begin{response}
  Section 4 has now included several additional sentences to clarify
  these points.
\end{response}
The correlations reported in section 4 (tables I-III) are overall
quite low (also compared to EDPM's r correlations for Chinese source
data in NIST's MetricsMATR challenge).  Could you comment on this?
\begin{response}
 [TO DO -- add a footnote]
\end{response}
For ease of lookup, please include in the table headings for tables
I-III that the correlations are with human judgments of adequacy and
fluency
\begin{response}
  Done.
\end{response}

In section 5.1, ``EDPM's strengths, relative to the other measures, are
particularly clear in the unstructured domains (wb and bc).''  This
statement does not seem to hold for EDPM vs. BLEU for the wb genre in
table Va; the correlation reported is the same for the two metrics?
\begin{response}
  The sentence at the end of the section is revised to indicate that
  ``in the unstructured domains (\texttt{wb} and \texttt{bc}), EDPM is
  always significantly better than at least one of the comparison
  baselines.''
\end{response}

@@

\section{Comments for the Author: Reviewer \#2}
\label{sec:reviewer2}

This article presents a method for evaluating MT system hypotheses
that is based on complete and partial dependency triple matches
between hypothesis and reference translation.

The paper is well motivated, clearly written, and presents interesting
results. On my opinion, it is suitable for publication with minor
revisions. 
\begin{response}
  Thank you for your detailed critique and many useful
  suggestions. Our responses are below:
\end{response}
My main points of criticism are:

### 2009-08-05 reviewers/review-response.tex

This article presents a method for evaluating MT system hypotheses
that is based on complete and partial dependency triple matches
between hypothesis and reference translation.

The paper is well motivated, clearly written, and presents interesting
results. On my opinion, it is suitable for publication with minor
revisions. 
\begin{response}
  Thank you for your detailed critique and many useful
  suggestions. Our responses are below:
\end{response}
My main points of criticism are:

\begin{itemize}
\item It is considerably too long. Papers are supposed to be 12 pages
  + references; this paper has more than 16 pages. I recommend (a)
  shortening the introduction; (b) shortening the discussion of the
  ``model space'' in Sections 2/3 somewhat; (c) removing the third
  experiment (Section 6), whose contribution is unclear to me,
  altogether. (see below for details)
  \begin{response}
    Our revisions incorporate many of these suggestions. Rather than
    eliminate section 6, we have chosen to compress it, but we have
    adopted the rest of the suggestions above.
  \end{response}

\item On the other hand, the paper does not motivate at all what the
  intuition behind the use of dependency triple match is. Why should
  we assume in the first place that dependency triples predict human
  judgments better than (e.g.) n-grams?
  \begin{response}
    We include an example in section 2 to address this point.  [TO DO
    -- using motivating examples?]
  \end{response}

\item Finally, the paper does not give a single example. In a paper
  about a novel evaluation metric, I would like to get a feeling for
  what it is that the new metric does better than existing
  metrics. (This can be addressed together with the previous point.)
  \begin{response}
    Done.
  \end{response}
\end{itemize}

@@

Detail comments:

\begin{itemize}
\item The discussion on page 2 reads nicely, but is probably too
  extensive -- in particular for a paper aimed at a special issue
  where there will presumably be an overview article that discusses
  relevant previous work.
  \begin{response}
    We have compressed this discussion considerably.
  \end{response}

\item  p.2, publically $\to$ publicly?
  \begin{response}
    Done.
  \end{response}

@@

\item  p.3, ``In section 2 etc.'' I'm not sure that a 12-page paper
  requires a table of contents.
  \begin{response}
    This section has also been compressed.
  \end{response}

\item  p.3, reference to Owczarzak et al.'s work. In particular since
  their work has also appeared in the MT journal (please update the
  reference, btw!), it would be good to expand on the similarities and
  differences of your work and theirs.
  \begin{response}
    [TO DO -- expand to rebuttal on expanding similarities and
    differences -- note that sec. 4 is essentially this].  The
    reference has been updated.
  \end{response}

### 2009-08-10 mtjournal.tex
revised figure to use only T,N,E features
Mari comments
Mari's revisions to title spacing and abstract

@@

\begin{document}
\begin{article}
\begin{opening}         
\title{Expected Dependency Pair Match:\\
Predicting translation quality with expected syntactic structure} 
\author{Jeremy G. \surname{Kahn}\email{jgk@u.washington.edu}}  
\institute{University of Washington}
\author{Matthew \surname{Snover}\email{snover@cs.umd.edu}}
\institute{University of Maryland}
\author{Mari \surname{Ostendorf}\email{ostendor@u.washington.edu}}  
\institute{University of Washington}
\runningauthor{Kahn, Snover \& Ostendorf}
\runningtitle{Expected Dependency Pair Match}
%s\date{May 10, 2009}

\begin{abstract}
  Recent efforts aimed at improving over standard machine translation
  evaluation methods (BLEU, TER) have investigated mechanisms for
  accounting for allowable wording differences either in terms of
  syntactic structure or synonyms/paraphrases. This paper explores an
  approach for combining scores from partial syntactic dependency
  matches with standard local n-gram matches using a statistical
  parser, and taking advantage of parse probabilities in deriving
  expected scores based on the N-best parses for the hypothesized
  sentence translation.  The new scoring metric, Expected Dependency
  Pair Match (EDPM), is shown to be superior to BLEU and TER in terms
  of correlation to human judgments and as a per-document and
  per-sentence predictor of HTER, using mean subtraction to account
  for document difficulty. Further, we explore the potential benefit
  of combining the n-gram and syntactic features of EDPM with the
  alternative wording features of TERp, with experiments showing that
  there is a benefit to accounting for syntactic structure on top of
  the semantic equivalency features.
\end{abstract}
\keywords{machine translation evaluation, syntax, dependency trees}

@@

% tuning target: weighted correlation with mean-removed segment HTER
\subsection{Effects of features on tuning}
% [we use weighted correlation to avoid emphasis on short segments
% (which hurts document-level and system-level utility) ]
In figure~\ref{fig:tuneresults}, we plot the Pearson's $r$ (with 95\%
confidence interval) for the results on the two test sets (each
trained on one and tested on the other).
\begin{figure}
  \begin{center}
    \includegraphics[scale=0.45]{tuning.eps}
  \end{center}
  \caption{Pearson's $r$ values for the two halves of the training
    set, with 95\% confidence intervals. }
  \label{fig:tuneresults}
\end{figure}
%
For each set of features, we plot the $r$ (and confidence) on both
halves of the corpus (for each half, tuned on the other half). In the
leftmost group of the figure, we include baselines: EDPM and BLEU and
TER (which are not tuned).  Next, the tuned E feature, which (by
itself) does not perform as well as TER or EDPM.
%
The remaining groups of three show that for each set of features, as E
(and EB) are included with others, correlation improves (though not
significantly).  These all move in the same direction. By the same
measurement, P features help beyond T -- as reported elsewhere -- but
N features do not seem to find a better correlation than TP features.
% MO suggestions:

>>>>

%%MO: changes other than compression
%% - changed notation for mean normalization in sect 5 to avoid confusion
%%   of two notions of mu
%% - moved tables out of the middle of paragraphs since that's visually
%%   easier for me to deal with in editing

@@

\begin{document}
\begin{article}
\begin{opening}         
\title{Expected Dependency Pair Match:
Predicting translation quality with expected syntactic structure} 
\author{Jeremy G. \surname{Kahn}\email{jgk@u.washington.edu}}  
\institute{University of Washington}
\author{Matthew \surname{Snover}\email{snover@cs.umd.edu}}
\institute{University of Maryland}
\author{Mari \surname{Ostendorf}\email{ostendor@u.washington.edu}}  
\institute{University of Washington}
\runningauthor{Kahn, Snover \& Ostendorf}
\runningtitle{Expected Dependency Pair Match}
%s\date{May 10, 2009}

\begin{abstract}
  Recent efforts to develop new machine translation
  evaluation methods have tried to 
  account for allowable wording differences either in terms of
  syntactic structure or synonyms/paraphrases. This paper primarily considers syntactic structure, combining scores from partial syntactic dependency
  matches with standard local n-gram matches using a statistical
  parser, and taking advantage of N-best parse probabilities in deriving
  scores for the hypothesized
  translation.  The new scoring metric, Expected Dependency
  Pair Match (EDPM), is shown to be superior to BLEU and TER in terms
  of correlation to human judgments and as a per-document and
  per-sentence predictor of HTER. Further, we combine the syntactic features of EDPM with the
  alternative wording features of TERp, showing a benefit to accounting for syntactic structure on top of
  semantic equivalency features.
\end{abstract}
\keywords{machine translation evaluation, syntax, dependency trees}

@@

% tuning target: weighted correlation with mean-removed segment HTER
\subsection{Effects of features on tuning}
% [we use weighted correlation to avoid emphasis on short segments
% (which hurts document-level and system-level utility) ]
In figure~\ref{fig:tuneresults}, we plot the Pearson's $r$ (with 95\%
confidence interval) for the results on the two test sets (each
trained on one and tested on the other).
\begin{figure}
  \begin{center}
    \includegraphics[scale=0.45]{tuning.eps}
  \end{center}
  \caption{Pearson's $r$ values for various feature tunings, with 95\%
    confidence intervals. BLEU$_4$ (add-one smoothed), TER, and EDPM
    scores are provided on the left for comparison.}
  \label{fig:tuneresults}
\end{figure}
%
For each set of features, we plot the $r$ (and confidence) on both
halves of the corpus (for each half, tuned on the other half). In the
leftmost group of the figure, we include baselines: EDPM and BLEU and
TER (which are not tuned).  Next, the tuned E feature, which (by
itself) does not perform as well as TER or EDPM.
%
The remaining groups of three show that for each set of features, as E
(and EB) are included with others, correlation improves (though not
significantly).  These all move in the same direction. By the same
measurement, P features help beyond T -- as reported elsewhere -- but
N features do not seem to find a better correlation than TP features.
% MO suggestions:
